---
title: "Economic Indicator comparison"
author: "ng"
date: "June 28, 2019"
output:
  html_document: default
---
## Overview

This is an RStudio shiny application developed as a part of final project in the Developing Data Products course. The app compares critical economic and internet performance indicators across 4 dimensions. 

The countries have been selected on the basis of representation across Europe and Asia and the app enab les a quick comparative analysis

## The Application includes the following:

- Form of Input used: Radio Button
- Reactive output displayed as a result of server calculations: The user (analyst) can select one or more dimensions to compare performance 
- The server.R and ui.R codes as well as dataset and Rmd files are posted on github at: <https://github.com/SuperVerkaufer/DATAPRODUCT>


```{r LoadPackages, include = FALSE}    
library(readxl)
```

## R Code for the Application

```{r, echo = TRUE, warning=FALSE}
library(shiny)

# Define UI for application that creates the radio buttons for selection of economic indcators
Perform <- read_excel("C:/Users/spencer.ng/Desktop/TH training/R Code Training MMM/Data products/GDPcountry.xlsx")

ui <- fluidPage(
  checkboxGroupInput("variable", "Variables:",
                     c("Population (K)" = "pop (K)",
                       "GDP (Bil)" = "IMFGDP (B)",
                       "Internet Population (Mil)" = "InternetPop (M)",
                       "Per Capita GDP" = "GdpPerCapita")),
  tableOutput("data")
)
# Application title
titlePanel("GDP Comparison")



# Define server logic required render the data table
server <- function(input, output) {
  output$data <- renderTable({
    Perform[, c("country", input$variable), drop = FALSE]
  }, rownames = TRUE)
}

# Run the application 
shinyApp(ui = ui, server = server)


```

